Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-08 thesis/paper.tex
Data col

%Consider adding subsub for code+doc and interviews later
\subsection{Data Collection} \label{data_collection}
%Intro to code inspection
The data were collected primarily through inspections of the source code and the archival analysis of the accompanying documentation. The source code was comprised of API versions. Each version of the API also had its own respective documentation. The documentation was inspected and organised to find explanations of the features offered by the API. ( "Not sure if this sentence fits here")

%Identify the changes
The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
%How the initial inspection was performed
The API code was inspected sequentially, starting with version 1.4. Both versions of the API underwent the same inspection. This involved extracting methods names, enums, data structures which were then subsequently stored in spreadsheets. Crosscase ( "Cross") analysis was then performed on both sets of data retrieved from different versions of the API \cite{seaman1999qualitative}. Changes were grouped into categories that best represented what the change achieved and were added to the spreadsheet. ( "add something here, following is not a full sentence") For example, additions, modifications and removals. After a change was found in the code, we identified the related documentation changes, or explanations that were relevant to that change and added them alongside their corresponding changes in the spreadsheets.

>>>>

%Consider adding subsub for code+doc and interviews later
\subsection{Data Collection} \label{data_collection}
%Intro to code inspection
The data were collected primarily through inspections of the source code and the analysis of accompanying documentation. The source code was comprised of the two API versions previously mentioned. Each version of the API had its own respective documentation, including example code, a library description and a basic development manual.

%Identify the changes
The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
%How the initial inspection was performed
The API code was inspected sequentially, starting with version 1.4. Both versions of the API underwent the same inspection. This involved extracting methods names, enums, data structures which were then subsequently stored in spreadsheets. Cross analysis was then performed on both sets of data retrieved from different versions of the API \cite{seaman1999qualitative}. Changes were grouped into categories that best represented what the change achieved and were added to the spreadsheet. After a change was found in the code, we identified the related documentation that offered explanations or descriptions relevant to that change that had occurred. Both the changes and the code were input into spreadsheets for further analysis.
